---
title: "ICES with R"
author: "Scott I. Large"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The purpose of this package is to create a simple and transparent workflow from ICES data portals to products that support the Advice process. Note that this package is not meant to re-invent the Advice process or circumnavigate proper databases... just to ensure a transparent and reproducible product. 

## Workflow

The ICES DATRAS web service is a simple and robust framework to search and retrieve data from the DATRAS databases. 

To Do: 
 Change the downloads to smaller chunks


## Vignette Info

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
